Automatically Proving Equivalence by Type-Safe Reflection

### 2017-03-22 paper-CICM-17/content/1-introduction.tex
Added paper for CICM-17

@@

When doing formal certification, we often require equality proofs between
terms.
For example, say we want to certify the function $f\ :\ A \rightarrow
B$. We have two functions $sem_A\ :\ A \rightarrow SEM$ and $sem_B\ : \ B
\rightarrow SEM$ which associate a semantics to each type A
and B. If this semantics describes all of the important properties of
the behaviour of $f$,
then the lemma of correctness of $f$ can be expressed as $forall\ a:A,\ semA\ a =
semB (f\ a)$. This situation happens very often in model transformations where the behaviour of an object has been preserved by some transformations, as for example in the CompCert certified compiler where the original C program and the generated assembly code are proven to have the same operational semantic \cite{Leroy09}.
Very often, the type $SEM$ has some algebraic
algebraic structure, and it becomes thus possible to
decide equalities in it by following some standard rewriting rules.  
All the equality symbols we have
encountered so far refer to the propositional equality. In the next section,
we will see how this is defined in Idris, and how it differs from the more
primitive judgemental equality.

>>>>

TO BE UPDATED LATER : (copied version from the older paper as a placeholder)

@@

When doing formal certification, we often require equality proofs between
terms.
For example, say we want to certify the function $f\ :\ A \rightarrow
B$. We have two functions $sem_A\ :\ A \rightarrow SEM$ and $sem_B\ : \ B
\rightarrow SEM$ which associate a semantics to each type A
and B. If this semantics describes all of the important properties of
the behaviour of $f$,
then the lemma of correctness of $f$ can be expressed as $forall\ a:A,\ semA\ a =
semB (f\ a)$. This situation happens very often in model transformations where the behaviour of an object has been preserved by some transformations, as for example in the CompCert certified compiler where the original C program and the generated assembly code are proven to have the same operational semantic \cite{Leroy09}.
Very often, the type $SEM$ has some algebraic 
structure, and it becomes thus possible to
decide equalities in it by following some standard rewriting rules.  
All the equality symbols we have
encountered so far refer to the propositional equality. In the next section,
we will see how this is defined in Idris, and how it differs from the more
primitive judgemental equality.
